Poseidon Adventure

### 2019-05-16 TestWeightAtStage.Rmd
formatting, add wtage html

---
title: "Testing atlantisom: visualize weight at (st)age output. How shall we interplolate this for true ages?"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

>ANNAGEBIO.nc: This output provides numbers in each annual age class (so mapped from Atlantis "age class" which can contain multiple years to true annual age classes). Set flag_age_output to 1 to get this output. Tracers provided are:
>   + Numbers at age per species
>
>ANNAGECATCH.nc: This output provides numbers at annual age class (so mapped from Atlantis "age class" which can contain multiple years to true annual age classes) in the catch and discards (summed over all fleets). Set flag_age_output to 1 to get this output. Tracers provided are:
>   + Numbers at age per species in the catch
>   + Numbers at age per species in the discards

>>>>

---
title: "Testing atlantisom: visualize weight at (st)age output. How should we interplolate this for true ages?"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

>**ANNAGEBIO.nc**: This output provides numbers in each annual age class (so mapped from Atlantis "age class" which can contain multiple years to true annual age classes). Set flag_age_output to 1 to get this output. Tracers provided are:
>
>   + Numbers at age per species
>
>**ANNAGECATCH.nc**: This output provides numbers at annual age class (so mapped from Atlantis "age class" which can contain multiple years to true annual age classes) in the catch and discards (summed over all fleets). Set flag_age_output to 1 to get this output. Tracers provided are:
>
>   + Numbers at age per species in the catch
>   + Numbers at age per species in the discards

### 2019-05-16 docs/index.Rmd
formatting, add wtage html

### Start age composition sampling: work in progress

@@

<a href="https://sgaichas.github.io/poseidon-dev/TestSmallestLength.html" target="_blank">Should there be small Greenland halibut in NOBA? - May 15, 2019</a>

>>>>

### Start age composition sampling: by output age class, not true age

@@

<a href="https://sgaichas.github.io/poseidon-dev/TestSmallestLength.html" target="_blank">Are length comps OK on the small end? - May 15, 2019</a>

May 16: Isaac says CCA fish look reasonable. NOBA Greenland halibut growth parameterization was reportedly "a nightmare" with conflicting science and datasets, so maybe we don't worry too much about them right now.

## Weight at age: by output age class, how to get to true age basis?

<a href="https://sgaichas.github.io/poseidon-dev/TestWeightAtStage.html" target="_blank">How much variability in weight at stage? - May 16, 2019</a>
